---
title: 'Assignment #8'
author: "Lorraine"
date: "March 30, 2019"
output: html_document
---

Task 1 & 2
```{r}
library(dplyr)
library(ggplot2)
library(readr)
library(tidytext)
library(stringr)
library(tidyr)
library(rvest)
library(udpipe)
library(scales)

urbanPlanning <- read_html("https://en.wikipedia.org/wiki/Urban_planning")
urbanDesign <- read_html("https://en.wikipedia.org/wiki/Urban_design")
urbanEconomics <- read_html("https://en.wikipedia.org/wiki/Urban_economics")
Architecture <- read_html("https://en.wikipedia.org/wiki/Architecture")


scrapeArticle <- function(url){
    title <- read_html(url) %>% 
        html_nodes(xpath='//*[@id="firstHeading"]/text()') %>% 
        html_text()
    
    
    text <- read_html(url) %>% 
        html_nodes(xpath = '//*[@id="content"]') %>% 
        html_nodes("p") %>% 
        html_text()
    
    tibble(title, text, section = 1:length(text))
}

urbanPlanning <- scrapeArticle("https://en.wikipedia.org/wiki/Urban_planning")    
urbanDesign <- scrapeArticle("https://en.wikipedia.org/wiki/Urban_design")
urbanEconomics <- scrapeArticle("https://en.wikipedia.org/wiki/Urban_economics")
Architecture <- scrapeArticle("https://en.wikipedia.org/wiki/Architecture") 

```

Task 3
```{r}

tidy_UP <- urbanPlanning %>% unnest_tokens(word,text) %>% 
    anti_join(stop_words) 
tidy_UD <- urbanDesign %>% unnest_tokens(word,text) %>% 
    anti_join(stop_words) 
tidy_Arch <- Architecture %>% unnest_tokens(word,text) %>% 
    anti_join(stop_words) 
tidy_UE <- urbanEconomics %>% unnest_tokens(word,text) %>% 
    anti_join(stop_words)

tidy_UP %>% count(word, sort=TRUE)
tidy_UD %>% count(word, sort=TRUE)
tidy_Arch %>% count(word, sort=TRUE)
tidy_UE %>% count(word, sort=TRUE)

tidy_UP %>%
  count(word, sort = TRUE) %>%
  filter(n > 4) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
    theme_minimal()

tidy_Arch %>%
  count(word, sort = TRUE) %>%
  filter(n > 9) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
    theme_classic()

tidy_UD %>%
  count(word, sort = TRUE) %>%
  filter(n > 6) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
    theme_minimal()

tidy_UE %>%
  count(word, sort = TRUE) %>%
  filter(n > 5) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
    theme_minimal()

```

Across the four graphs, the main topic (i.e. urban planning, urban design..etc) names are the most frequent. Some frequent common words shared include: design, century, city, and social.   

Task 4
```{r}
df_text <- rbind(tidy_UP, tidy_Arch)
tidy_text_UE <- rbind(df_text, tidy_UE)
tidy_text <- rbind(tidy_text_UE, tidy_UD)
final_tidy_text <- tidy_text[c("title","word")]

frequency <- final_tidy_text %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>% 
  count(title, word) %>% 
  group_by(title) %>% 
  mutate(proportion = n / sum(n)) %>%  
  select(-n) %>% 
  spread(title, proportion) %>% 
  gather(title, proportion, 2:4) 

frequency


frequency %>% ggplot(aes(x = proportion, 
                         y = `Urban planning`)) +
    geom_abline(color = "gray40", lty = 2) +
    geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
    geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
    scale_x_log10(labels = percent_format()) +
    scale_y_log10(labels = percent_format()) +
    scale_color_gradient(limits = c(0, 0.001), low = "darkslategray4", high = "gray75") +
    facet_wrap(~title, ncol = 2) +
    theme(legend.position="none") + 
    theme_minimal() +
    labs(y = "Urban planning", x = NULL)
```

We can see that "approach" and "academic" is shared between the articles of Architecture and Urban Design when we plot it against Urban Planning. As for Urban Economics there were some errors that might have rigged the graph because "th" is not a word and analyzing and analysis are not significantly different.

Task 5
```{r}
text_join <- rbind(urbanDesign, urbanEconomics)
text_add <- rbind(text_join, urbanPlanning)
textdf <- rbind(text_add, Architecture)
textDF <- textdf[c("title", "text")]
textDF

model <- udpipe_download_model(language = "english-ewt")
udmodel_english <- udpipe_load_model(file = file.path("english-ewt-ud-2.3-181115.udpipe"))
UP_DF<- udpipe::udpipe_annotate(udmodel_english, urbanPlanning$text) %>% data.frame()
UD_DF<- udpipe::udpipe_annotate(udmodel_english, urbanDesign$text) %>% data.frame()
UE_DF<- udpipe::udpipe_annotate(udmodel_english, urbanEconomics$text) %>% data.frame()
Arch_DF<- udpipe::udpipe_annotate(udmodel_english, Architecture$text) %>% data.frame()

UP_DF$phrase_tag <- as_phrasemachine(UP_DF$upos, type = "upos") # convert parts of speech tags to one letter tags
stats <- keywords_phrases(x = UP_DF$phrase_tag, term = tolower(UP_DF$token), #Here are the combinations of keywords we want to collect
                          pattern = "(A|N)*N(P+D*(A|N)*N)*", 
                          is_regex = TRUE, detailed = FALSE) %>% 
    subset(ngram > 1 & freq > 3)
stats %>%
    slice(1:20) %>% 
    ggplot(aes(x = reorder(keyword, freq), y = freq))+ 
    geom_col(fill = "blue") + coord_flip() + 
    ylab("Keywords") +
    xlab("Frequency")+
    theme_minimal() + 
    ggtitle("Top Noun Phrases")
```

```{r}
UD_DF$phrase_tag <- as_phrasemachine(UD_DF$upos, type = "upos") # convert parts of speech tags to one letter tags
stats <- keywords_phrases(x = UD_DF$phrase_tag, term = tolower(UD_DF$token), #Here are the combinations of keywords we want to collect
                          pattern = "(A|N)*N(P+D*(A|N)*N)*", 
                          is_regex = TRUE, detailed = FALSE) %>% 
    subset(ngram > 1 & freq > 3)
stats %>%
    slice(1:20) %>% 
    ggplot(aes(x = reorder(keyword, freq), y = freq))+ 
    geom_col(fill = "pink") + coord_flip() + 
    ylab("Keywords") +
    xlab("Frequency")+
    theme_minimal() + 
    ggtitle("Top Noun Phrases")
```

```{r}
UE_DF$phrase_tag <- as_phrasemachine(UE_DF$upos, type = "upos") # convert parts of speech tags to one letter tags
stats <- keywords_phrases(x = UE_DF$phrase_tag, term = tolower(UE_DF$token), #Here are the combinations of keywords we want to collect
                          pattern = "(A|N)*N(P+D*(A|N)*N)*", 
                          is_regex = TRUE, detailed = FALSE) %>% 
    subset(ngram > 1 & freq > 3)
stats %>%
    slice(1:20) %>% 
    ggplot(aes(x = reorder(keyword, freq), y = freq))+ 
    geom_col(fill = "red") + coord_flip() + 
    ylab("Keywords") +
    xlab("Frequency")+
    theme_minimal() + 
    ggtitle("Top Noun Phrases")
```

```{r}
Arch_DF$phrase_tag <- as_phrasemachine(Arch_DF$upos, type = "upos") # convert parts of speech tags to one letter tags
stats <- keywords_phrases(x = Arch_DF$phrase_tag, term = tolower(Arch_DF$token), #Here are the combinations of keywords we want to collect
                          pattern = "(A|N)*N(P+D*(A|N)*N)*", 
                          is_regex = TRUE, detailed = FALSE) %>% 
    subset(ngram > 1 & freq > 3)
stats %>%
    slice(1:20) %>% 
    ggplot(aes(x = reorder(keyword, freq), y = freq))+ 
    geom_col(fill = "green") + coord_flip() + 
    ylab("Keywords") +
    xlab("Frequency")+
    theme_minimal() + 
    ggtitle("Top Noun Phrases")
```

Interestlingly, Architecture and Urban Design articles shared the most frequent keyword of "urban design". Aside from the top, most frequent keyword being the topic of the article, we can see that across all four articles, the top keywords were vastly different. 
